---
title: Bootstrap Confidence Intervals with Differential Privacy
authors:
  - name: Marcel Neunhoeffer
    department: Department of Computer Science
    affiliation: Boston University
    location: Boston, MA
    email: marceln@bu.edu
  - name: Adam D. Smith
    department: Department of Computer Science
    affiliation: Boston University
    location: Boston, MA
    email: ads22@bu.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - Bootstrap
  - Differential Privacy
  - Statistical Inference
bibliography: references.bib
biblio-style: unsrt
output: rticles::arxiv_article
---

# Introduction

Here goes an introduction text

# Our proposed method
\label{sec:method}
Similar to Dan Sheldon 
Instead of focusing on a single quantitiy of interest we produce synthetic data in the form of a private cdf and apply the same mechanism on resamples of the private cdf (post-processing) to get a bootstrapped distribution of private cdfs and calculate confidence intervals for several statistics of interest (such as quantiles, e.g. the median.)

Tree based algorithm by 

# Related Work



# Experiments

We evaluate the performance of our proposed method in a set of experiments. In these experiments 

We 


Datasets: Normal, mixtures of normals (different weights)

adult, census PUMS (ipums), (business?)

We consider the full data set as ground truth and take simple random samples from it to evaluate our proposed method.

Parameters: N, epsilon, B (fixed to start with?)

Evaluation:

Statistics of interest: Median, mean, some percentile, entire cdf --> CI around it!

How do we evaluate it. We calculate the empirical coverage across repeated samples.^[We take these counts as ground truth. Our comparison is between the results of our method and the statistic of interest in the entire sample. This is different from an inference to the population statistic of interest.]

# Notes

Different possibilities to get quantiles 

The range needs to be set properly (how?), otherwise truncation will bias results.

You can use directly LaTeX command or Markdown text. 

LaTeX command can be used to reference other section. See Section \ref{sec:headings}.
However, you can also use **bookdown** extensions mechanism for this.



## Headings: second level

You can use equation in blocks

$$
\xi _{ij}(t)=P(x_{t}=i,x_{t+1}=j|y,v,w;\theta)= {\frac {\alpha _{i}(t)a^{w_t}_{ij}\beta _{j}(t+1)b^{v_{t+1}}_{j}(y_{t+1})}{\sum _{i=1}^{N} \sum _{j=1}^{N} \alpha _{i}(t)a^{w_t}_{ij}\beta _{j}(t+1)b^{v_{t+1}}_{j}(y_{t+1})}}
$$

But also inline i.e $z=x+y$

### Headings: third level

Another paragraph. 


# Examples of citations, figures, tables, references
\label{sec:others}

You can insert references. Here is some text [@kour2014real; @kour2014fast] and see @hadash2018estimate.

The documentation for \verb+natbib+ may be found at

You can use custom blocks with LaTeX support from **rmarkdown** to create environment.

::: {.center latex=true}
  <http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}>
:::

Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  

You can insert LaTeX environment directly too.

\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}

produces

\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}


## Figures

You can insert figure using LaTeX directly. 

See Figure \ref{fig:fig1}. Here is how you add footnotes. [^Sample of the first footnote.]

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{4cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
  \label{fig:fig1}
\end{figure}

But you can also do that using R.

```{r fig2, fig.cap = "Another sample figure"}
plot(mtcars$mpg)
```

You can use **bookdown** to allow references for Tables and Figures.


## Tables

Below we can see how to use tables. 

See awesome Table~\ref{tab:table} which is written directly in LaTeX in source Rmd file.

\begin{table}
 \caption{Sample table title}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
  \label{tab:table}
\end{table}

You can also use R code for that.

```{r}
knitr::kable(head(mtcars), caption = "Head of mtcars table")
```


## Lists

- Item 1
- Item 2 
- Item 3
